### 2014-06-19 reports/report.Rmd
Update reports to use new tables names

**Data contributor:** `r .dat$contact$name`.

**Email:** `r .dat$contact$email`.

**Address:** `r .dat$contact$address`.

@@

Data for `r length(.dat$data$dataset)` individuals from `r length(unique(.dat$data$location))` locations covering `r length(unique(.dat$data$species))` species.

>>>>

**Data contributor:** `r .dat$contacts$name`.

**Email:** `r .dat$contacts$email`.

**Address:** `r .dat$contacts$address`.

@@

Data for `r length(.dat$data$studyName)` individuals from `r length(unique(.dat$data$location))` locations covering `r length(unique(.dat$data$species))` species.
